%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {bFan Sports} % Organization
    {New York, N.Y.} % Location
    {June 2015 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed systems and features with a focus on fan engagement and asset management for sports teams and clubs.}
        \item {Did code review and helped manage pull requests to major company repositories.}
        \item {Helped grow the platform to where it is today: almost 50 European sports clubs using the product with a combined total of more than 70,000 user accounts.}
        \item {Worked with multiple web technologies on an Amazon Web Services stack.}
        \begin{itemize}
          \item {AngularJS: The front end of the team administration portal is built with AngularJS, with plans to move to a more modern version of Angular in the future.}
          \item {PHP: The administration portal uses CodeIgniter and PHP for its routing and database interaction. Additionally, many daemons and tasks to help keep services running are built in PHP using Symphony.}
          \item {Python: Our mobile API is run on a serverless stack using Lambda and API Gateway. All the functionality for the Lambda functions is coded using Python to access other AWS assets.}
        \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer, Co-Founder, CTO} % Job title
    {Knearn} % Organization
    {New York, N.Y.} % Location
    {June 2013 - April 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented websites for educational and professional mentorship.}
        \begin{itemize}
          \item {Initially built with a PHP backend on a standard LAMP stack.}
          \item {Later converted to Meteor.js to make the experience much more interactive and responsive.}
        \end{itemize}
        \item {Led and managed a small team of developers aiming to develop features using an agile methodology.}
        \item {Worked with business team to come up with solutions and marketing for the project.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Intern} % Job title
    {McKinsey \& Company} % Organization
    {New York, N.Y.} % Location
    {January 2014 – May 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Performed software performance and usage testing to determine fit for use in the company.}
        \item {Used experience with SharePoint to give insight to corporate social networking software and file sharing systems.}
        \item {Branded software distributions within the company using CSS.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technical Analyst Intern} % Job title
    {AvePoint} % Organization
    {Jersey City, N.J.} % Location
    {January 2012 – May 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided remote assistance troubleshooting company software via phone, email, or remote connection.}
        \item {Debugged environments using Microsoft SharePoint, Microsoft SQL Server, Microsoft Server, and other similar products.}
        \item {Made simple tools to automate office procedures using raw JavaScript.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Intern} % Job title
    {McKinsey \& Company} % Organization
    {New York, N.Y.} % Location
    {June 2011 – August 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Prepared servers and environments used company wide with UNIX based web software (LAMP, Rails, etc).}
        \item {Worked with vendors to get their software running on these servers and customized/configured for use.}
        \item {Used software supplied APIs to do migrations of files between versions of user systems.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
